\documentclass[12pt]{article}
\usepackage{anyfontsize}
\usepackage{calc}
\usepackage{enumitem}
\usepackage{fontspec}
\setmainfont{Times New Roman}

\title{willekeslresume}

%% Create a new rule to fill remaining text line with underline
\newlength{\remaining}
\newcommand{\titleline}[1]{
\setlength{\remaining}{\textwidth-\widthof{\textsc{#1}}}
\noindent\underline{\textsc{#1}\hspace*{\remaining}}\par}
%%


\begin{document}
{
	\noindent{\large{\underline{\textbf{Lourens Willekes}}}} | lourw95@gmail.com

	\vspace{\baselineskip}
	\titleline{\textbf{EDUCATION}}
    \noindent\textbf{Grand Valley State University} \hfill Fall 2018
    
    \noindent Bachelor of Science in Engineering; Computer Engineering \hfill GPA: 3.9
    
    \vspace{\baselineskip}
    \noindent\textbf{Coursework} - System Programming; Data Structures and Algorithms; Operating Systems Concepts; Embedded System Design; Design of Microcontroller Applications
    
    \noindent\textbf{Computer Skills} - C/C++; CNTK; Python; Java; Git/SVN; Linux/Unix; JIRA
    
    \vspace{\baselineskip}
    \titleline{\textbf{EXPERIENCE}}
    \noindent\textbf{Grand Valley / Active Inspection} \hfill 2016 - 2017
    \begin{itemize}[noitemsep]
    	\item Helped develop an application to build, train, and evaluate deep neural networks for use in Active Inspections' inspection systems.
    \end{itemize}
    
    \noindent\textbf{DornerWorks Ltd} \hfill 2015 - 2016
    \begin{itemize}[noitemsep]
    	\item Worked on a bug fixing team and updated requirements for GE's Aircraft Health Management System.
    	\item Gained experience interacting directly with customers to solve problems with their systems.
    	\item Tested and verified firmware commands for X-Rite Intellitrax.
    	\item Designed functions and created a test device for Dexter Laundry's Drying Machine. Wrote Python code to interpret C structures for the DAQ unit.
    	\item Maintained continuous integration testing for Xen hypervisor on the Zynq platform.
    \end{itemize}
    
    \noindent\textbf{Thunder Mountain Holdings} \hfill 2011 - 2014
    \begin{itemize}[noitemsep]
    	\item Managing/working with a team on busy days, as well as handling the site individually at other times.
    	\item Extensive experience dealing with customers and meeting their expectations.
    	\item Meticulous when necessary, pay attention to detail well.
    \end{itemize}

    \bigskip
    %\titleline{\textbf{REFERENCES}}
    \hrule
	\bigskip
    \noindent References available upon request.
      
}

{\noindent}
\end{document}